\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\Huge Nate Livarchuk}\\[6pt]
    Ringgold, Georgia \quad | \quad Bilingual: English \& Ukrainian\\
    Email: \href{mailto:your.email@example.com}{your.email@example.com} \quad | \quad LinkedIn: \href{https://linkedin.com/in/yourprofile}{linkedin.com/in/yourprofile}
\end{center}

\vspace{1em}

\section*{Resume Summary}
A motivated and proactive individual with a diverse background in automotive repair, e-commerce, digital content creation, and information technology. Currently pursuing IT certifications in system administration, networking, and cloud technologies. Driven by strong work ethic, analytical skills, and a passion for continuous learning.

\section*{Top Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Content Creation \& Social Media:} 250+ automotive YouTube videos (55.9K subscribers, 8.89M views), TikTok growth (Hunan Wok: 43,575 followers; personal: 120,489 followers).
  \item \textbf{Automotive Repair \& E-commerce:} Hands-on expertise in maintenance, rebuilds, collision repair. Created 1,500+ optimized eBay listings. Skilled in product photography, SEO, inventory.
  \item \textbf{Information Technology:} Pursuing certifications in networking, sysadmin, cloud. Proficient in MS Office, Adobe Suite, WordPress. Applied IT to streamline operations.
  \item \textbf{Bilingual Communication:} Fluent English \& Ukrainian. Strong written and verbal communication.
\end{itemize}

\section*{Key Achievements}
\begin{itemize}[leftmargin=*]
  \item \textbf{Maxiroe Project:} VIN-based automotive parts catalog \& search engine with JIT inventory and automated data scraping.
  \item \textbf{VTDAutoParts (2023–Present):} Optimized eBay listings and streamlined inventory management.
  \item \textbf{Twenty Third Garage (2021–2023):} Built YouTube to 55.9K subs, 8.89M views, 250+ videos.
  \item \textbf{Hunan Wok (2022–Present):} Managed TikTok, grew to 43,575 followers and 1.32M hearts.
  \item \textbf{Certified Auto Repair (2018–2021):} Maintenance, part installs, and collision repair in family-owned shop.
\end{itemize}

\section*{Education \& Training}
Currently pursuing IT certifications in networking, system administration, and cloud technologies.

\section*{Background}
Born and raised in Ringgold, Georgia to a Ukrainian immigrant family. Bilingual in English and Ukrainian, committed to growth and effective teamwork.

\end{document}
